Continuous gravitational waves in the lab: recovering audio signals with a table-top~optical microphone

### 2021-11-15 paper/finalSubmission/JGardnerManuscript/JGardner.tex
moving author list into main tex adding build script for submission

%\documentclass[aps,pra,superscriptaddress,reprint]{revtex4-2}
\documentclass[prb,preprint]{revtex4-2}

@@

\input{authorList.tex}

@@

In this appendix, we demonstrate that the modulus of the Fourier transform is an appropriate detection statistic when searching for a sinusoidal signal in Gaussian noise. 
We describe the data as
\begin{equation}
x(t) = s(t) + n(t)\,, 
\label{eqn:GNdata}
\end{equation}
where $s(t)$ and $n(t)$ are the signal and noise, respectively.
The signal takes the form
\begin{equation}
s(t) = A \cos\left[{\omega t + \phi}\right]\,,
\label{eqn:GNmodel}
\end{equation}
where $A$, $\omega$, and $\phi$ are the amplitude, angular frequency and phase of the signal, respectively. 
The noise $n(t)$ is a fluctuating zero-mean time series with the following property: if we define an inner product between two arbitrary time series $u(t)$ and $v(t)$ as 
\begin{equation}
\ip{u}{v} = \frac{1}{T} \int_0^T \mathrm{d} t \, u(t) v(t)\,,
\label{eqn:ipuv}
\end{equation}
where $T$ is the total time of the observation, then the likelihood $\mathcal{L}$ of measuring the noise-noise product $\ip{n}{n}$ is given by 
\begin{equation}
\mathcal{L} = \exp\left( -\frac{1}{2}\ip{n}{n}\right)\,.
\label{eqn:ipnn}
\end{equation}
Equations~\ref{eqn:ipuv} and~\ref{eqn:ipnn} define what it means for noise to be Gaussian through the fundamental measurement of $\ip{n}{n}$.

>>>>

\documentclass[aps,pra,superscriptaddress,reprint]{revtex4-2}

@@

\author{James~W.~Gardner}
\email{james.gardner@anu.edu.au}
\affiliation{%
Centre for Gravitational Astrophysics, The Australian National University, Acton, ACT, 2601, Australia
}
\affiliation{%
OzGrav-ANU, Australian Research Council Centre of Excellence for Gravitational Wave Discovery, The Australian National University, Acton, ACT, 2601, Australia
} 
\affiliation{%
School of Physics, University of Melbourne, Parkville, Victoria, 3010, Australia
}

\author{Hannah~Middleton}
\email{hannah.middleton@unimelb.edu.au}
\affiliation{%
School of Physics, University of Melbourne, Parkville, Victoria, 3010, Australia
}
\affiliation{%
Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria, 3122, Australia 
}
\affiliation{%
OzGrav-Melbourne, Australian Research Council Centre of Excellence for Gravitational Wave Discovery, Parkville, Victoria, 3010, Australia
}

\author{Changrong~Liu}
\email{changrongl1@student.unimelb.edu.au}
\affiliation{%
Department of Electrical and Electronic Engineering, University of Melbourne, Parkville, Victoria, 3010, Australia
}
\affiliation{%
OzGrav-Melbourne, Australian Research Council Centre of Excellence for Gravitational Wave Discovery, Parkville, Victoria, 3010, Australia
}

\author{Andrew~Melatos}
\email{amelatos@unimelb.edu.au}
\affiliation{%
School of Physics, University of Melbourne, Parkville, Victoria, 3010, Australia
}
\affiliation{%
OzGrav-Melbourne, Australian Research Council Centre of Excellence for Gravitational Wave Discovery, Parkville, Victoria, 3010, Australia
}

\author{Robin~Evans}
\affiliation{%
Department of Electrical and Electronic Engineering, University of Melbourne, Parkville, Victoria, 3010, Australia
}
\affiliation{%
OzGrav-Melbourne, Australian Research Council Centre of Excellence for Gravitational Wave Discovery, Parkville, Victoria, 3010, Australia
}

\author{William~Moran}
\affiliation{%
Department of Electrical and Electronic Engineering, University of Melbourne, Parkville, Victoria, 3010, Australia
}

\author{Deeksha~Beniwal}
\affiliation{%
Department of Physics, The University of Adelaide, South Australia, 5005, Australia
}
\affiliation{%
The Institute of Photonics and Advanced Sensing (IPAS), The University of Adelaide, South Australia, 5005, Australia
}
\affiliation{%
OzGrav-Adelaide, Australian Research Council Centre of Excellence for Gravitational Wave Discovery, South Australia, 5005, Australia
}

\author{Huy~Tuong~Cao}
\affiliation{%
Department of Physics, The University of Adelaide, South Australia, 5005, Australia
}
\affiliation{%
The Institute of Photonics and Advanced Sensing (IPAS), The University of Adelaide, South Australia, 5005, Australia
}
\affiliation{%
OzGrav-Adelaide, Australian Research Council Centre of Excellence for Gravitational Wave Discovery, South Australia, 5005, Australia
}

\author{Craig~Ingram}
\affiliation{%
Department of Physics, The University of Adelaide, South Australia, 5005, Australia
}
\affiliation{%
The Institute of Photonics and Advanced Sensing (IPAS), The University of Adelaide, South Australia, 5005, Australia
}
\affiliation{%
OzGrav-Adelaide, Australian Research Council Centre of Excellence for Gravitational Wave Discovery, South Australia, 5005, Australia
}

\author{Daniel~Brown}
\affiliation{%
Department of Physics, The University of Adelaide, South Australia, 5005, Australia
}
\affiliation{%
The Institute of Photonics and Advanced Sensing (IPAS), The University of Adelaide, South Australia, 5005, Australia
}
\affiliation{%
OzGrav-Adelaide, Australian Research Council Centre of Excellence for Gravitational Wave Discovery, South Australia, 5005, Australia
}

\author{Sebastian~Ng}
\affiliation{%
Department of Physics, The University of Adelaide, South Australia, 5005, Australia
}
\affiliation{%
The Institute of Photonics and Advanced Sensing (IPAS), The University of Adelaide, South Australia, 5005, Australia
}
\affiliation{%
OzGrav-Adelaide, Australian Research Council Centre of Excellence for Gravitational Wave Discovery, South Australia, 5005, Australia
}

@@

In this appendix, we demonstrate that the modulus of the Fourier transform is an appropriate detection statistic when searching for a sinusoidal signal in Gaussian noise. 
We describe the data as
\begin{equation}
x(t) = s(t) + n(t)\,, 
\label{eqn:GNdata}
\end{equation}
where $s(t)$ and $n(t)$ are the signal and noise, respectively.
The signal takes the form
\begin{equation}
s(t) = A \cos\left[{\omega t + \phi}\right]\,,
\label{eqn:GNmodel}
\end{equation}
where $A$, $\omega$, and $\phi$ are the amplitude, angular frequency and phase of the signal, respectively. 
The noise $n(t)$ is a fluctuating zero-mean time series with the following property: if we define an inner product between two arbitrary time series $u(t)$ and $v(t)$ as 
\begin{equation}
\ip{u}{v} = \frac{1}{T} \int_0^T \mathrm{d} t \, u(t) v(t)\,,
\label{eqn:ipuv}
\end{equation}
where $T$ is the total time of the observation, then the probability $\mathcal{L}$ of measuring the noise-noise product $\ip{n}{n}$ is given by 
\begin{equation}
\mathcal{L} = \exp\left( -\frac{1}{2}\ip{n}{n}\right)\,.
\label{eqn:ipnn}
\end{equation}
Equations~\ref{eqn:ipuv} and~\ref{eqn:ipnn} define what it means for noise to be Gaussian through the fundamental measurement of $\ip{n}{n}$.
